### 2018-03-16 paper.Rmd
gender

>>>>

```{r}
stats <- get_speaker_statistics(role = "Target_Child")

data <- stats %>%
  filter(!is.na(target_child_sex), collection_name == "Eng-NA") %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  summarise(ttr = sum(num_types) / sum(num_tokens))

ggplot(data, aes(x = target_child_age, y = ttr, color = target_child_sex)) +
  geom_smooth()
```
